Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2018-05-15 automatica/paper.tex
address abate's comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

The median run-time for \note{the successful} benchmarks is 6.6\,s for the fixed-point and 5.45\,s for floating-point implementations, respectively.  
We consider these times short enough to be of practical use to control engineers, and thus affirm the validity of EG1.

There are \note{a few [you mean half!]} instances for which both approaches fail to synthesise a controller.  
For the multi-stage approach, the completeness threshold may be too large, thus causing a timeout.  
On the other hand, the abstraction-based approach may require a very precise abstraction, resulting in too many refinements and, consequently, again in a timeout.  
Yet another source of incompleteness is the inability of the {\sc synthesize} phase to use a large enough precision for
the plant model.

>>>>

The median run-time for \textcolor{blue}{the successful} benchmarks is 6.6\,s for the fixed-point and 5.45\,s for floating-point implementations, respectively.  
We consider these times short enough to be of practical use to control engineers, and thus affirm the validity of EG1.

\textcolor{blue}{Both approaches fail to synthesise a controller half of the instances.}  
For the multi-stage approach, the completeness threshold may be too large, thus causing a timeout.  
On the other hand, the abstraction-based approach may require a very precise abstraction, resulting in too many refinements and, consequently, again in a timeout.  
Yet another source of incompleteness is the inability of the {\sc synthesize} phase to use a large enough precision for
the plant model.
